Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-23 paper/virtual_cytoplasm_v2.tex
Wrote more on discussion and started conclusion

Structure and dynamics of biomolecules are well characterized {\em in vitro}, however these studies {\em in vivo} are still evolving. 
Investigating biomolecular properties {\em in vivo} is possible through developments in the fields of nuclear magnetic resonance~\cite{reckel2007,pielak2008}, or fluoroscence spectroscopies~\cite{ignatova2004,xie2008,English2011}.
An alternative method is to use computational models and simulation techniques. Biomolecular simulations are often carried out under dilute conditions or simple models of macromolecular crowdings~\cite{Spiga2014a,Harada2012a,Nawrocki2017a}. However, more attemps in modeling bacterial cytoplasm have been made recently~\cite{Mcguffee2010,Yu2016a}.

@@

\begin{table}
\centering
\begin{tabular}{ l c c }
\hline
\multirow{2}{*}{Protein} & 	\multicolumn{2}{c}{Fraction [\%]} \\
& Absolute & Cumulative \\ 
\hline
TufA & 19.7 & 19.7 \\
MetE & 11.6 & 31.4 \\
IcdA & 4.7  & 36.1 \\
AhpC & 4.1  & 40.2 \\
CspC & 4.0  & 44.2 \\
Ppa  & 2.9  & 47.0 \\
GapA & 2.1  & 49.1 \\
Eno  & 1.9  & 51.1 \\
\hline
\end{tabular}
\caption{Absolute and cumulative fraction of the total abundance of non-ribosomal proteins in the cytosol of {\em E. coli} K12 to which each protein that was selected to compose our cytoplasm model corresponds to.}
\label{tbl:protein_fraction}
\end{table}

\subsubsection{RNA fraction}
Transporter RNAs (tRNAs) account for 74\% of the dry weight of non-ribosomal RNAs. Thus, we chose to model the RNA presence in the cytoplasm with tRNA molecules. Specifically, we considered the tRNA(Phe) molecule as a representative of tRNAs due to the availability of a recent crystallographic structure~\cite{Byrne2015}.
The protein and RNA content of the total dry weight of \textit{E.coli} is 55\% and 2.9\%, respectively. That is, the total RNA weight corresponds to 5\% of the total protein weight. This protein/RNA weight ratio was used to calculate the correct number of tRNA(Phe) molecules that were added to the cytoplasm model \colorbox{red!50}{(Table XXX)}.

@@

\subsubsection{Inorganic ions fraction}
Finally, Mg\textsuperscript{2+} was used as counter-ions for tRNA and ATP. KCl was added to neutralize the charges of the simulation box and to reach the ionic strength of 0.150 mol/L by substution of randomly selected water molecules.

@@

\subsection{The effect of crowded systems}

@@

Under crowded conditions, molecules are constrained to a smaller volume due to collisions with the other components of the crowded environment. This extent of this effect is evident when we compare the translational diffusion constant of each component in the cytoplasm model, $D_{cyto}$, and in a dilute system, $D_{dil}$ (Figure~\ref{fig:translational_diffusion}A). The ration of these quantities is independent of the protein size and is always close to 0.13 (Figure~\ref{fig:translational_diffusion}B). However, the effect of crowding over the translation diffusion of tRNA is two times higher, indicating that its movement is specially constrained in the crowded environment.

\begin{figure}[H]
\includegraphics[scale=0.5]{msd.pdf}
\includegraphics[scale=0.5]{diff_cyto_over_singles.pdf}
\caption{A)Diffusion coefficient of crowders from single molecule simulations (blue bars) and cytoplasm simulations (orange bars). B) The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis.}
\label{fig:translational_diffusion}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_RNA_metabolites.pdf}
\caption{Radial distribution function showing the probability of finding metabolites or cations around RNA molecules in the cytoplasm model.}
\label{fig:tRNA_aggregation}
\end{figure}

@@

\caption{A) Solvent accessible surface area (sasa) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average sasa for each protein in single molecule simulation is over number of chains of proteins and three replica. The average sasa for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors. B) Root mean squared displacement (rmsd) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average rmsd for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{oligomer.pdf}
\caption{Inter-chain hydrogen bonds (hb) for oligomers from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average hydrogen bonds for each oligomer in single molecule simulation is over number of chains and three replica. The average hydrogen bonds for each oligomer in cytoplasm simulation is over number of appearance of the chain in the oligomer in three replica. The error bars show the standard errors.}
\end{figure}

@@

\subsubsection{Structural dynamics}
Proteins are slighly more flexible in the crowded environment. Root mean square fluction (RMSF) calculations show that the flexibility profile of the proteins is not affected by crowding, except in the cases in which there are conformational changes, TufA ... as shown before (Figure~\ref{fig:rmsf}). This is in agreement with our results showing that the structural integrity of the proteins is not significantly affected. In addition to that, our results show that the proteins are slighly more flexible in the crowded environment than in the dilute condition (Figure~\ref{fig:rmsf}). This is likely due to the nonspecific interations and collisions that often happen under crowding conditions \cite{aasd}.

\begin{figure}[H]
\includegraphics[scale=0.5]{rmsf_2cols.pdf}
\caption{Root mean squared fluctuations (rmsf) for 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues for each chain of proteins. The average rmsf for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\label{fig:rmsf}
\end{figure}

@@

We found that completely protonating the phosphate groups of ATP and FBP is enough prevent their aggregation with Mg$^{2+}$ (Figure~\ref{fig:avoiding_aggregation}). While RDFs show that ATP$^{-3}$ and FBP$^{-4}$ aggregate around Mg$^{2+}$, this is not observed for ATPH\textsubscript{3} and FBPH\textsubscript{4}. \colorbox{red!50}{We further tested this hypothesis by simulating a system composed by tRNA, FBP, ATP and Mg$^{2+}$. In this setup, protonating ATP and FBP was also enough to avoid aggregation with Mg$^{2+}$ and the metabolites didn't aggregated around tRNA, which acts as a source of Mg$^{2+}$.}

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_mg.pdf}
\caption{Radial distribution function (rdf) showing the probability of finding a metabolite or an RNA around MG2+. The inset plot shows the rdf for short distance ($ r < 0.6 \,\, nm$)}
\label{fig:avoiding_aggregation}
\end{figure}

@@

\begin{itemize}
  \item Use of force field should be taken with care due to aggregation that was reported repeatedly. We used AMBER scaled force field for protein water interaction. In other atomistic model of Mycoplasma genitalium, the CHARRM scaled protein water interaction was used for the same reason.
\end{itemize}

@@

\colorbox{blue!50}{ $<<$ Discuss the translational diffusion results: }

Diffusion coefficient of crowders from single molecules to cytoplasm are decreased in a range of 84\% (Ppa) to 93\% (tRNA) (Fig.~\ref{fig:translational_diffusion} A). The fitted line with the slope close to zero  ($m = 0.00028$) shows that the drop in diffusion coefficient is independent of the size of the proteins. The largest drop of diffusion coefficient corresponds to tRNA and we found that the aggregation of ATP$^{-3}$ and FBP$^{-4}$ around Mg$^{2+}$ which was used as cation for tRNA leads to its confinement. In fact, by removing diffusion coefficient of tRNA from the data points the slope of the line decreases by half ($m=0.00014$). Our finding on the drop of diffusion coefficient is closely in line with {\em in vivo}. The translational diffusion coefficient of Green Fluorescent Protein (GFP) in {\em E. coli} that was measured by fluorescence revovery after photobleaching (FRAP) was decreased 90\% comparing to {\em in vitro} measurement~\cite{Elowitz1999,Konopka2006}.

\colorbox{blue!50}{what is the meaning of the straight line in D/D0? Is this expected? }

\colorbox{blue!50}{Is this in agreement/disagreement with which models/theories? $>>$ }

HARD SPHERE THEORETICAL MODEL PREDICTs THE DROP IN DIFFUSION COEFFICIENT AS A FUNCTION OF VOLUME AVAILABLE TO PARTICLES. THEREFORE, THE VOLUME AVAILABLE TO OUR PROTEINS IN OUR MODEL WOULD BE THE SAME IF THE SIMULATION IS LONG ENOUGH FOR ALL PROTEINS TO SPAN THE WHOLE SPACE.

 \begin{itemize}
  \item No significant structural changes (such as unfoldin or partial unfolding) can be seen from properties such as sasa (fig 5), and gyration radius  (WE HAVEN'T ADD THIS FIG, SHALL WE?).
  \item inter-chain hydrogen interactions. 
  \item  intermolecular protein protein interactions can be seen in forms of  rmsd (fig 4) and rmsf (fig 6). As proteins interact with their environment, their structure flutuate more than in dilute cases. However, the effect is not large enough to cause unfolding (fig 5, and gyration)
  \item rmsf in all cases are higher for crowders in cytoplasm than in dilute codition
  \item RMSFs for cyto have higher statistical error ! (even if we have more copies in cyto.) e.g. crowder-n5
  \item NOT SURE ABOUT THIS: THE FACT THAT METABOLITES ARE POLYMERIZED DOES NOT SABOTAGE THE WHOLE SIMULATION AND WE STIL COULD ANALYSE THE SIMULATION AND GET MEANINGFUL OUTCOME, AND THIS WOULD NOT (MOST PROBABLY) BE AFFECTED BY NON-CLUSTERED METABOLITE. INDEED WE DID NOT ANALYZE CHEMICAL OR DYNAMIC PROPERTIES OF METABOLITES
 \end{itemize}

\section*{Conclusions}\label{sec:dissc}

\bibliography{library}
% \begin{addendum}
%  \item  
%  \item[Competing Interests] 
%  \item[Correspondence]  
% \end{addendum}

>>>>

Structure and dynamics of biomolecules are well characterized {\em in vitro}, however these studies {\em in vivo} are still evolving. 
Investigating biomolecular properties {\em in vivo} is possible through developments in the fields of nuclear magnetic resonance~\cite{reckel2007,pielak2008}, or fluoroscence spectroscopies~\cite{ignatova2004,xie2008,English2011}.

An alternative method is to use computational models and simulation techniques. Biomolecular simulations are often carried out under dilute conditions or simple models of macromolecular crowdings~\cite{Spiga2014a,Harada2012a,Nawrocki2017a}. However, more attemps in modeling bacterial cytoplasm have been made recently~\cite{Mcguffee2010,Yu2016a}.

@@

\begin{table}[H]
\centering
\begin{tabular}{ l c c }
\hline
\multirow{2}{*}{Protein} & 	\multicolumn{2}{c}{Fraction [\%]} \\
& Absolute & Cumulative \\ 
\hline
TufA & 19.7 & 19.7 \\
MetE & 11.6 & 31.4 \\
IcdA & 4.7  & 36.1 \\
AhpC & 4.1  & 40.2 \\
CspC & 4.0  & 44.2 \\
Ppa  & 2.9  & 47.0 \\
GapA & 2.1  & 49.1 \\
Eno  & 1.9  & 51.1 \\
\hline
\end{tabular}
\caption{Absolute and cumulative fraction of the total abundance of non-ribosomal proteins in the cytosol of {\em E. coli} K12 to which each protein that was selected to compose our cytoplasm model corresponds to.}
\label{tbl:protein_fraction}
\end{table}

\subsubsection{RNA fraction}
Transporter RNAs (tRNAs) account for 74\% of the dry weight of non-ribosomal RNAs \colorbox{red!50}{REF}. Thus, we chose to model the RNA presence in the cytoplasm with tRNA molecules. Specifically, we considered the tRNA(Phe) molecule as a representative of tRNAs due to the availability of a recent crystallographic structure~\cite{Byrne2015}.
The protein and RNA content of the total dry weight of \textit{E.coli} is 55\% and 2.9\%, respectively \colorbox{red!50}{REF}. That is, the total RNA weight corresponds to 5\% of the total protein weight. This protein/RNA weight ratio was used to calculate the correct number of tRNA(Phe) molecules that were added to the cytoplasm model \colorbox{red!50}{(Table XXX)}.

@@

\subsubsection{Inorganic ions fraction}
Finally, Mg\textsuperscript{2+} was used as counter-ions for tRNA and ATP. K$^{+}$ and Cl$^{-}$ were added to neutralize the charges of the simulation box and to reach the ionic strength of 0.150 mol/L by substution of randomly selected water molecules.

@@

\subsection{Effects of macromolecular crowding}

@@

Under crowded conditions, molecules are constrained to a smaller volume due to collisions with the other components of the crowded environment. The extent of this effect is evident when we compare the translational diffusion constant of each component in the cytoplasm model, $D_{cyto}$, and in a dilute system, $D_{dil}$ (Figure~\ref{fig:translational_diffusion}A). The ratio of these quantities is independent of the protein size and is always close to 0.13 (Figure~\ref{fig:translational_diffusion}B). However, the effect of crowding over the translation diffusion of tRNA is two times higher. Its $D_{cyto}/D_{dil}$ is 0.07, indicating that its movement is specially constrained in the crowded environment (Figure~\ref{fig:translational_diffusion}B, crowder with 25 kDa).

\begin{figure}[H]
\includegraphics[scale=0.5]{msd.pdf}
\includegraphics[scale=0.5]{diff_cyto_over_singles.pdf}
\caption{A)Diffusion coefficient of crowders from single molecule simulations (blue bars) and cytoplasm simulations (orange bars). B) The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis. \textbf{\color{red}{THE Dcyto/Ddil PLOT IS "SQUEEZED" BECAUSE OF ITS STRANGE SCALE. IT WOULD BE BETTER TO CENTER THE DATAPOITS, E.G. USE THE Y-AXIS RANGE OF 0.0-0.2 OR SOMETHING SIMILAR. THIS SCALE WILL MAKE THE DIFFERENCE OF THE BEHAVIOR OF tRNA MORE VISIBLE AS WELL}}}
\label{fig:translational_diffusion}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_RNA_metabolites.pdf}
\caption{Radial distribution function showing the probability of finding metabolites or cations around RNA molecules in the cytoplasm model.\color{red}\textbf{THIS PLOT NEEDS REVISION. I DON'T SEE ERROR BARS (HOW WAS STATISTICS DONE FOR THE RDFs?).I SUBMITTED NEW RDF CALCULATIONS CENTERED AROUND tRNA BECAUSE I DIDN'T FIND THE XVG FILES THAT WERE USED TO GENERATE THIS PLOT}}
\label{fig:tRNA_aggregation}
\end{figure}

@@

\caption{A) Solvent accessible surface area (sasa) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average sasa for each protein in single molecule simulation is over number of chains of proteins and three replica. The average sasa for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors. B) Root mean squared displacement (rmsd) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average rmsd for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.\textbf{\color{red}{THE MEASUREMENT NAME, SASA AND RMSD, IS MISSING IN THE Y-AXIS OF BOTH PLOTS}}}
\label{fig:structural_integrity_chain}
\end{figure}

@@

%\begin{figure}[H]
%\includegraphics[scale=0.5]{oligomer.pdf}
%\caption{Inter-chain hydrogen bonds (hb) for oligomers from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average hydrogen bonds for each oligomer in single molecule simulation is over number of chains and three replica. The average hydrogen bonds for each oligomer in cytoplasm simulation is over number of appearance of the chain in the oligomer in three replica. The error bars show the standard errors.}
%\end{figure}

@@

\subsubsection{Structural dynamics}
Proteins are slighly more flexible in the crowded environment. Root mean square fluction (RMSF) calculations show that the flexibility profile of the proteins is not affected by crowding, except in the cases in which there are conformational changes, TufA ... as shown before (Figure~\ref{fig:rmsf}). This is in agreement with our results showing that the structural integrity of the proteins is not significantly affected. In addition to that, our results show that the proteins are slighly more flexible in the crowded environment than in the dilute condition (Figure~\ref{fig:rmsf}). This is likely due to the nonspecific interations and collisions that often happen under crowding conditions \textbf{\color{red}{REF}}.

\begin{figure}[H]
\includegraphics[scale=0.5]{rmsf_2cols.pdf}
\caption{Root mean squared fluctuations (rmsf) for 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues for each chain of proteins. The average rmsf for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.\textbf{\color{red}{CAN YOU ADD THE PROTEIN NAME AS A LABEL INSIDE EACH PLOT? I THINK THE VARIABLE NAME SHOULD BE IN THE Y-AXIS (RMSF NM2)}}}
\label{fig:rmsf}
\end{figure}

@@

We found that completely protonating the phosphate groups of ATP and FBP is enough prevent their aggregation with Mg$^{2+}$ (Figure~\ref{fig:avoiding_aggregation}). While RDFs show that ATP$^{-3}$ and FBP$^{-4}$ aggregate around Mg$^{2+}$, this is not observed for ATPH\textsubscript{3} and FBPH\textsubscript{4}.

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_mg.pdf}
\caption{Radial distribution function (rdf) showing the probability of finding a metabolite or an RNA around MG2+. The inset plot shows the rdf for short distance ($ r < 0.6 \,\, nm$) \color{red}{\textbf{HOW WAS STATISTICS DONE FOR THE RDFs? I DON'T SEE ERROR BARS}}}
\label{fig:avoiding_aggregation}
\end{figure}

@@

The main difference between the behavior of the macromolecules that compose our model in the crowded system and in the dilute condition is their translational diffusion coefficient, which drops by more around 85\% for the proteins and 93\% for the tRNA (Fig.~\ref{fig:translational_diffusion} A). The slope of a linear regression over values of $D_{cyto}/D_{dil}$ is close to zero ($m = 0.00028$), showing that the drop in diffusion coefficient is independent of the size of the macromolecules. We found that the aggregation of ATP$^{-3}$ and FBP$^{-4}$ around Mg$^{2+}$, which was used as cation for tRNA, leads to its exaggerated confinement. Thus, tRNA is considered as an outlier in our cytoplasm model. In fact, by removing diffusion coefficient of tRNA from the data points of $D_{cyto}/D_{dil}$, the slope of the line changes by 50\% and gets even closer to zero ($m=0.00014$). These results are in agreement with experimental results showing that the translational diffusion coefficient of Green Fluorescent Protein (GFP) in {\em E. coli}, as measured by fluorescence recovery after photobleaching (FRAP), decreased 90\% when compared to {\em in vitro} measurements~\cite{Elowitz1999,Konopka2006}.

It has been demonstrated that each of the force fields that are most widely used to perform molecular dynamics simulations of macromolecules have different results for highly concentrated amino acid solutions ~ \cite{andrews2013molecular}. Previous all-atom simulations of high scale cytoplasm models used parameters from the CHARMM family of force fields ~\cite{Yu2016,Mcguffee2010}. In this work we used, for the first time, the AMBER family of force fields to perform all-atom explicit solvent of a cytoplasm model for the total of \SI{3}{\micro\second}.

Except for some local unfolding for TufA, all crowders were stable during the simulations (Figure \ref{fig:structural_integrity_chain} and their flexibility profile doesn't change significantly (Figure \ref{fig:rmsf}. This shows that our cytoplasm model is stable even in the microsecond range.

\textbf{\color{red}{MISSING RESULTS: WHOLE CROWDER STRUCTURAL INTEGRITY USING BURIED OLIGOMER AREA}}

However, we observed aggregation of Mg, ATP and FBP...

\section*{Conclusions}\label{sec:concl}

In this work we built a cytoplasm model...

the model was validated by reproducing experimental data about the reduction of the translational diffusion coefficient of proteins in E.coli.

the model is stable.

however, aggregation!

@@

\bibliography{library}

% \begin{addendum}
%  \item  
%  \item[Competing Interests] 
%  \item[Correspondence]  
% \end{addendum}
